Relative Stable Maps in Genus One via Central Alignments

### 2018-03-24 genus-one-relative-maps.tex
Almost finished proof

It remains to consider the case when $E$ is a wheel of rational components. Again the Gathmann-like condition (1) ensures we have balancing on the level of $\Pic(E)$, once we show that all the $u_q$ for the nodes internal to $E$ are integers.

>>>>

It remains to consider the case when $E$ is a wheel of rational components. Again the Gathmann-like condition (1) ensures we have balancing on the level of $\Pic(E)$, once we show that all the $u_q$ for the nodes internal to $E$ are integers. Labelling the components of $E$ as $C_1,\ldots,C_k$ with $C_i$ intersecting $C_{i-1}$ and $C_{i+1}$, we obtain relations:
\begin{equation*} u_{q_i} r_{q_i} = \gamma_{i+1} - \gamma_{i-1} \end{equation*}
Thus $u_{q_i} \in r_{q_i}^{-1} \cdot \Z$. But if we restrict $\Lcal$ to each component and look at the resulting equation, we see that in fact $u_{q_i} \in (1/r_{q_j}) \Z$ for all $j$. Thus $u_{q_i} \in (1/g) \Z$ where $g = \operatorname{gcd}(r_{q_1},\ldots,r_{q_k})$. \basenote{Maybe we can fix this using saturation: note that we only need a map from the saturation of the quotient to $\N$, not from the quotient itself.}
